Uncertainty Quantification and Inference of Manning's Friction Coefficient using DART Buoys Data during \tohoku Tsunami

### 2014-02-02 friction_paper/coefs.tex

\begin{equation} 
p(n_1,n_2,n_3,\sigma^2 | \vec d) 
\propto \frac{1}{\sqrt{2 \pi \sigma^2}} 
 \prod_{i=1}^m  
\exp \left\lbrace \frac{-(d_i - G_i)^2}{2 \sigma^2} \right\rbrace
\ p(\sigma^2)p(n_1)p(n_2) p(n_3).
\label{eq:post_coef}
\end{equation}

To complete the definition of the posterior, we need to choose proper priors that should be based 
on some \emph{a priori} knowledge about the parameters. In our case, a uniform
prior for all three Manning's $n$ parameters is assumed, with $n_i$ in the range  $[0.005,0.2]$; therefore:

\begin{equation} 
p(n_i) = \begin{cases}
		\displaystyle \frac{1}{0.2-0.005} &\text{for~} 0.005 <  n_i \leq 0.2 ,  \\
		0 &\text{otherwise}.
\end{cases}
\end{equation}
Regarding the variance, the only information we know 
is that $\sigma^2$ is always positive.
We thus assume a Jeffreys prior \citep{sivia} for $\sigma^2$, expressed as:

\begin{equation} 
p(\sigma^2) =  \begin{cases}
		\displaystyle \frac{1}{\sigma^2} &\text{for~} \sigma^2 > 0,  \\
		0 &\text{otherwise}. 
		\end{cases}.
\label{eq:var_pr}
\end{equation}

>>>>

\begin{equation} 
\Pi(n_1,n_2,n_3,\sigma^2 | \vec d) 
\propto \frac{1}{\sqrt{2 \pi \sigma^2}} 
 \prod_{i=1}^m  
\exp \left\lbrace \frac{-(d_i - G_i)^2}{2 \sigma^2} \right\rbrace
\ q(\sigma^2)q(n_1)q(n_2) q(n_3).
\label{eq:post_coef}
\end{equation}

To complete the definition of the posterior, we need to choose proper priors that should be based 
on some \emph{a priori} knowledge about the parameters. In our case, a uniform
prior for all three Manning's $n$ parameters is assumed, with $n_i$ in the range  $[0.005 - 0.2]$; therefore:

\begin{equation} 
q(n_i) = \begin{cases}
		\displaystyle \frac{1}{0.2-0.005} &\text{for~} 0.005 <  n_i \leq 0.2 ,  \\
		0 &\text{otherwise}.
\end{cases}
\end{equation}
Regarding the noise variance, the only information we know 
is that $\sigma^2$ is always positive.
We thus assume a Jeffreys prior \citep{sivia} for $\sigma^2$, expressed as:

\begin{equation} 
q(\sigma^2) =  \begin{cases}
		\displaystyle \frac{1}{\sigma^2} &\text{for~} \sigma^2 > 0,  \\
		0 &\text{otherwise}. 
		\end{cases}.
\label{eq:var_pr}
\end{equation}
